Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-08-09 paper.tex
Minor updates.

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter paticle mass of 2001 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit 
\citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 
0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables 
having their usual definitions. The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue. At this point, about 20\% of the volume is over 10\% ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39. \textbf{Throughout the rest of the paper, all numbers are in physical units.}

>>>>

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter paticle mass of 2001 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. \jhw{Add refinement criteria.} The simulation is 
initialized with \music{} \citep{Hahn11_MUSIC} at $z = 130$ and uses the cosmological parameters from the Planck collaboration best fit 
\citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 
0.6825, $\Omega_{\rm DM}$ = 0.2685, and $h = 0.6711$, with the variables 
having their usual definitions. The simulation is run until $z = 9.32$, when it becomes too computationally expensive to continue. At this point, about 20\% of the volume is over 10\% ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39. \textbf{Throughout the rest of the paper, all numbers are in physical units.}

### 2019-08-09 referee.tex
Minor updates.

We chose this threshold to be similar to the density that would trigger another level of AMR past our maximum level of 12.  This density can be calculated as \textbf{(give calculation and density value at level 13)}.

>>>>

We chose this threshold to be similar to the density that would trigger another level of AMR past our maximum level of 12.  At these scales, the grid is primarily refined from the Jeans length criterion, which is resolved by at least 8 cells.  At $T=300$ K, the Jeans length is $L_{\rm J} = 0.17$~pc at $\rho = 10^6 m_{\rm H}$~g/cm$^3$.  \textbf{JHW: finish this point.}
